### 2016-08-25 section/5_exper.tex
finish shrinking

\paragraph{Implementation and Platform}
We implement \Tool in LLVM-3.4.2 \cite{llvm}, and conduct our
%Our implementation consists of 17654 lines of C++ code, 
%with 4748 for instrumenter, 674 for resultless analysis, 
%5802 for redundancy analysis, 
%and the remaining 6430 for common utilities. 
experiments on a i5-3330S machine, with Linux 3.19 kernel.

\paragraph{Benchmarks}
Note that \Tool is a tool that helps diagnose already-manifested performance problems,
not a detection tool that can help predict not-yet-manifested
problems. Consequently, our benchmarks are performance problems that have already
happened in real world, and we will reproduce these problems to evaluate \Tool.
To conduct a thorough evaluation, we use
benchmarks from two different sources.

First, we evaluate \Tool on all bugs, 18 in total, that we can reproduce 
among the 45 bugs listed in Table \ref{tab:root}. 
Among these 18, seven are extracted from Java or JavaScript
programs and re-implemented in C++, as \Tool currently only handles C/C++
programs; one is extracted from a very old version of Mozilla that can no longer be
compiled as it is.
%These 18 bugs include all the benchmarks used in the recent
%statistical performance debugging work~\cite{SongOOPSLA2014}.
%The extraction is conducted by XXX.
When we extract code, we try our best to keep all bug-related data structures,
caller functions, and callee functions intact, and re-implement them in C++, 
following the original data flow and control flow. For these extracted benchmarks, 
we design bug-triggering inputs for them based on the bug-triggering inputs in 
the original bug reports and the mapping relationship between inputs of original programs 
and re-implemented programs.
Overall, these 18 bugs cover a wide variety of inefficiency root causes, as 
shown in Table~\ref{tab:benchmarks}. 
We will refer to this set of bugs as our \emph{general} benchmark suite.

Note that, we expect \Tool algorithm to also work for the remaining 27 bugs 
listed in Table \ref{tab:root}, but they are too difficult to be reproduced.
First, they all depend on 
special hardware/software environment that our machines are not equipped with.
For example, some bugs can only be triggered on Windows, and some depend on 
.Net libraries. 
Furthermore, the bug-related code for these 27 cases
cannot be easily extracted or reimplemented, as we did for the eight 
benchmarks mentioned above. 
For example, some bugs are related to GUI widgets, which are too complicated to 
re-implement or emulate. As another example, some bugs' inefficient 
loops traverse big graphs. Although we can extract the buggy code regions, it is 
too difficult to figure out the bug-triggering inputs
(i.e., the graphs) without reproducing the original bugs.

%Second, we evaluate \Tool on 21 out of the 42 detected by Toddler \cite{Alabama, toddlerbuglist}.
%{\color{red} We use all benchmarks that are reported with bug-triggering inputs and fixed by developers. 
%All of these bugs come from Java programs. 
%We extract XXX (how did you
%extract exactly?) and re-implement in C++. Each extracted benchmark 
%contains 4--5 loops (how come you always have 4--5 loops??XXX). 
Second, we evaluate \Tool on Toddler~\cite{Alabama, toddlerbuglist} benchmark suite.
Toddler project provides the bug-triggering inputs and detailed explanation
for 21 inefficient-loop bugs that have been confirmed and fixed by developers, and
we evaluate \Tool on \emph{all} of these 21 bugs.
Due to the focus of Toddler, all of these bugs 
are related to misusing basic data structures in Java, like ArrayList, HashSet, 
HashMap, and LinkedList. We extract these bugs and re-implemented them in 
C/C++, following the procedure discussed above. In doing so,
we also re-implement basic Java data structures following a recent version of 
\texttt{openjdk}. At the end, each extracted benchmark contains at least five
loops, except for two cases where only four loops exist in the extracted version.

We use Toddler benchmark suite for two reasons.
First, it provides a large set of 
repeatable inefficient loop problems that we can access. 
Second, it was set up for a completely different reason and with a different 
methodology from our
\emph{general} benchmark suite,
and hence can well complement the \emph{general} suite.
We should also note that, Toddler focuses on inefficient nested loops, and hence its
benchmark bugs only cover two types of inefficiency root causes,
as shown in Table \ref{tab:benchmarks}.

\paragraph{Metrics}
Our experiments are designed to evaluate \Tool from three main aspects:
(1) 
\textit{Coverage}. Given our benchmark suite that covers a wide variety
of real-world root causes, can \Tool identify all those root causes?
(2)
\textit{Accuracy}. 
When analyzing non-buggy loops, will \Tool generate any false positives?
(3) 
\textit{Performance}.
What is the run-time overhead of \Tool?

\paragraph{Evaluation settings}
Our evaluation uses existing statistical performance diagnosis
tool \cite{SongOOPSLA2014} to process a performance problem and identify 
one or a few suspicious loops for \Tool to analyze.
For all but four benchmarks, statistical debugging identifies the
real root-cause loop as the most suspicious loop. For the remaining four
benchmarks, which all come from Table \ref{tab:root},
the real root-cause loops are ranked number 2, 2, 4, and 10.
%Overall, we believe future tools can accurately identify the most one or a couple
%of suspicious loops.
%XXX (what can we say about Toddler benchmark set here?)

@@

For all benchmarks we use, real-world
users have provided at least one problem-triggering input in their on-line 
bug reports. We use these inputs in our run-time analysis.

As discussed in Section \ref{sec:design}, our analysis contains 
several configurable thresholds. In our evaluation,
we use 0.001 as the \textit{resultful rate} threshold for identifying
0*1? 
%loops, 0.01 as the \textit{resultful rate} threshold for identifying 
and [0$|$1]* resultless loops; we use 
0.5 as the \textit{redundancy rate} threshold for identifying redundant loops.
%, and 
%2 as the \textit{cross-iteration redundancy rate} (i.e., 
%the number of distinct iterations is less than half of the total iterations).

All the analysis and performance results presented below regarding
cross-loop analysis is obtained using $1/100$ sampling rate; all the
results regarding cross-iteration analysis is obtained using $1/1000$ sampling
rate. We use sparser sampling rate in the latter case, because there tend to
be more loop iterations than loop instances.
All our diagnosis results require only \textbf{one} run under the 
problem-triggering input.

More discussions about all the parameters/thresholds presented above, including
how to set them and how sensitive they are, are discussed in Section
\ref{sec:sensi}.

\subsection{Coverage Results}
\label{sec:coverage}
Overall, \Tool provides good diagnosis coverage, as shown by the check-marks in Table~\ref{tab:benchmarks}
(the ``Did \Tool Identify ..?'' columns). 
\Tool identifies the correct root cause for \textbf{all} \allbugs benchmarks, and 
suggests fix strategies that exactly match what developers took in practice
for 33 out of \allbugs cases.

@@

Second, the fix strategy taken by developers is related to but not exactly the same as
what suggested by \Tool.
The root-cause loops in 
Collections bugs \#407, \#408, and \#425 all conduct frequent linear searches in arrays.
\Tool suggests data-structure changes for these three cases. Developers' patches 
still keep the original data structures and the original buggy loops, but they
did use hash-sets, which contain the same content as the arrays do,
to help conditionally skip the loops.

Third, \Tool cannot suggest fix strategy for 1* loops.
For GCC\#12322, \Tool correctly tells that the loop under study
does not contain any form of inefficiency and produce results in every 
iteration, and hence fails to suggest any fix strategy. In practice, GCC
developers decide to skip the loop, which will cause some programs compiled by
GCC
to be less performance-optimal than before. However, GCC developers feel
that it is worthwhile considering the slow-down caused by the original loop.

@@

As shown in Table \ref{tab:performance}, 
the performance of \Tool is good. The overhead is consistently under or around 5\% 
except for one benchmark, Mozilla\#347306. We believe \Tool is promising for potential production
run usage.
We can easily further lower the overhead through sparser sampling.
As we will discuss later, 
the current diagnosis results are obtained by running the
program only \textbf{once} under the problem-triggering workload.
If we use sparser sampling, more failure runs will be needed to obtain good
diagnosis results.

@@

The performance benefit of sampling is huge.
Without sampling, redundancy
analysis lead to over 100X slowdown for six benchmarks.

The benefit of static optimization is also non-trivial. 
For example, for MySQL\#15811 and MySQL\#27287, static analysis alone can
judge that they do not contain cross-iteration redundancy: the computation of 
each iteration depends on loop induction variables, which are naturally different
in different iterations. Consequently, run-time overhead is completely
eliminated for these two benchmarks.
As another example, the buggy loops of MySQL\#27287 and MySQL\#15811 access 
arrays. 
After changing to tracking the initial and ending memory-access addresses
of the array, instead of the content of the whole array accesses,
the overhead is reduced from 12.18\% to 0.20\% for MySQL\#27287, 
and from 20.53\% to 0.35\% for MySQL\#15811 respectively 
(sampling is conducted consistently here).

\subsection{Parameter Setting and Sensitivity}
\label{sec:sensi}
\paragraph{Sampling rates}
We have tried different sampling rates for redundancy analysis.
Intuitively, sparser sampling leads to lower overhead but worse diagnosis
results. Due to space constraints, we briefly summarize the results below.

When we lower the sampling rate from 1/100 to 1/1000 
in cross-loop redundancy analysis,
among all the benchmarks in Table \ref{tab:performance},
Mozilla\#416628 incurs the largest overhead (merely 4.51\%). 
The diagnosis results remain the same for all but
GCC\#12322, where too few samples are available
to judge redundancy.

When we lower the sampling rate from 1/1000 to 1/10000
in cross-iteration redundancy analysis,
among all the benchmarks in Table \ref{tab:performance},
Mozilla\#347306 has the largest overhead (merely 7.38\%). 
%In fact, Mozilla347306 is the only one whose overhead is larger than 2\%. 
The diagnosis results remain 
the same for all but GCC\#12322.
%If we increase the sampling rate to 1/100, we will 
%have two benchmarks whose overhead is larger than 30\%.

\paragraph{Resultful and redundancy rate}
Since the severity of resultless and redundant loops depends on
workload, it is natural that \Tool uses two thresholds in its diagnosis.
In fact, the diagnosis results are largely {\bf in}sensitive to the threshold
setting. For example, the results would remain the same when
changing the redundancy rate threshold from 0.5 to any value between about
0.1 and 0.66. We will have 1 more false negative and 1 fewer benign false positive, 
when the rate is 0.7. The trend is similar for resultless
loop checking. 
%XXX

Our default setting %is obtained based on our experience
should work for many problems.
Developers can adjust these thresholds. 
They can even get rid of thresholds, and only
use the raw values of resultful/redundancy rates to understand
the absolute and relative (in)efficiency nature of suspicious 
loops. Based on our experiments, the difference between efficient and inefficient
loops is usually obvious, based on these rates.

\subsection{Comparison with other tools}

Automated tools have been developed to detect inefficient loop bugs
\cite{Alabama, CARAMEL, IsilDillig.PLDI15}. 
As discussed in Section \ref{sec:intro}, although these tools are very
useful, they are not designed for failure diagnosis. 
For example, Toddler~\cite{Alabama} only targets inefficient nested loops, and
hence can only cover about half of the bugs in our \emph{general} benchmark suite.
Being a dynamic tool, it also incurs 10X or more slowdowns, which is much more
expensive than \Tool. 
Caramel~\cite{CARAMEL} statically detects inefficient loops that can be fixed
by adding conditional-breaks. Very few bugs in Table \ref{tab:root} are like this.
CLARITY~\cite{IsilDillig.PLDI15} statically detects redundant traversal bugs, 
which arise if a program fragment repeatedly iterates over a data structure, such as an array or list, that has not been modified between successive traversals of the data structure.
Like Toddler, it targets nested loops.
We expect it to detect a sub-set of the cross-loop redundancy
loops and a sub-set of 0*1? resultless loops in our benchmark set.
In summary, \Tool aims to explain performance problems that have 
already manifested,
yet bug detection tools aim to predict problems that may not have manifested.
They are suitable for different usage scenarios.

Comparing with existing profiling and performance
statistical debugging technique \cite{SongOOPSLA2014}, \Tool provides much
more detailed root-cause information. Instead of just identifying loops that
are highly correlated-with/responsible-for the execution slowness, \Tool
can accurately point out whether these suspicious loops are efficient or not,
and which type of inefficiency a loop contains, if any, and make fix suggestions.

>>>>

\noindent\textbf{Implementation and Platform}
We implement \Tool in LLVM-3.4.2 \cite{llvm}, and conduct our
%Our implementation consists of 17654 lines of C++ code, 
%with 4748 for instrumenter, 674 for resultless analysis, 
%5802 for redundancy analysis, 
%and the remaining 6430 for common utilities. 
experiments on a i5-3330S machine, with Linux 3.19 kernel.

\noindent\textbf{Benchmarks}
\Tool is a diagnosis tool that helps understand and fix 
already-manifested performance problems,
not a detection tool that help predict not-yet-manifested
problems. Consequently, our benchmarks are performance problems that have already
happened in real world, and we will reproduce them to evaluate \Tool.
For a thorough evaluation, we use
benchmarks from two different sources.

First, \emph{general} benchmark suite.
We evaluate \Tool on all bugs, 18 in total, that we can reproduce 
among the 45 bugs discussed in Section \ref{sec:eval_taxonomy}. 
These 18 bugs cover a wide variety of inefficiency root causes, as 
shown in Table~\ref{tab:benchmarks}. 
We use the problem-triggering inputs reported by real-world
users in \Tool run-time analysis.
Among these 18, seven are extracted from Java/JavaScript
programs.
%, as \Tool currently only handles C/C++
%programs; one is extracted from a very old version of Mozilla that can no longer be
%compiled as it is.
%These 18 bugs include all the benchmarks used in the recent
%statistical performance debugging work~\cite{SongOOPSLA2014}.
%The extraction is conducted by XXX.
For these benchmarks, we did our best to keep all bug-related data structures
and caller/callee functions intact, and re-implement them in C++
following the original data and control flow. 
%Their
%bug-triggering inputs are produced based on the bug-triggering inputs in 
%the original bug reports.

Note that, we expect \Tool to also work for most, if not all, of 
the remaining 27 bugs listed in Table \ref{tab:root}.
However, these 27 bugs are too difficult to be reproduced, as they 
depend on special hardware/software environment (e.g., Windows OS and 
.Net libraries) and cannot be easily extracted or reimplemented. 
For example, some bugs are related to GUI widgets, which are too complicated to 
re-implement. Some bugs' inefficient 
loops traverse big graphs, whose bug-triggering inputs
(i.e., the graphs) are difficult to figure out 
without reproducing the original bugs.

%Second, we evaluate \Tool on 21 out of the 42 detected by Toddler \cite{Alabama, toddlerbuglist}.
%{\color{red} We use all benchmarks that are reported with bug-triggering inputs and fixed by developers. 
%All of these bugs come from Java programs. 
%We extract XXX (how did you
%extract exactly?) and re-implement in C++. Each extracted benchmark 
%contains 4--5 loops (how come you always have 4--5 loops??XXX). 
Second, we evaluate \Tool on Toddler~\cite{Alabama, toddlerbuglist} benchmark suite.
Toddler project provides the bug-triggering inputs and detailed explanation
for 21 inefficient-loop bugs that have been confirmed and fixed by developers, and
we evaluate \Tool on \emph{all} of them.
Due to the focus of Toddler, all of these bugs are caused by inefficient
\textit{nested} loops and only cover two types of inefficiency root causes,
as shown in Table \ref{tab:benchmarks}.
We extract these bugs and re-implemented them in 
C/C++;
we also re-implement basic Java data structures following a recent version of 
\texttt{openjdk}. Each extracted benchmark contains at least five
loops, except for two that contain four loops each.

The general benchmark suite and Toddler benchmark suite both provide
a large set of repeatable inefficient loop problems that we can access. 
At the same time, they were initially set up for different reasons and
methodologies,
and hence well complement each other.
All the benchmarks led to severe performance problems.
After developers fixed these problems, the performance of each benchmark improves
4X -- 500X under the user-reported workload in our experiments.

\noindent\textbf{Evaluation settings}
Our evaluation uses existing statistical performance diagnosis
tool \cite{SongOOPSLA2014} to process a performance problem and identify 
one or a few suspicious loops for \Tool to analyze.
For all but four benchmarks, statistical debugging identifies the
real root-cause loop as the most suspicious loop. For the remaining four
benchmarks, which all come from Table \ref{tab:root},
the real root-cause loops are ranked number 2, 2, 4, and 10.
%Overall, we believe future tools can accurately identify the most one or a couple
%of suspicious loops.
%XXX (what can we say about Toddler benchmark set here?)

@@

We use 0.001 as the default \textit{resultful rate} threshold for identifying
0*1? 
%loops, 0.01 as the \textit{resultful rate} threshold for identifying 
and [0$|$1]* resultless loops; we use 
0.5 as the default \textit{redundancy rate} threshold for identifying redundant loops.
%, and 
%2 as the \textit{cross-iteration redundancy rate} (i.e., 
%the number of distinct iterations is less than half of the total iterations).
We use $1/100$ sampling rate for cross-loop redundancy analysis and 
$1/1000$ sampling rate for cross-iteration redundancy analysis
(there tend to be more loop iterations than loop instances).
All our diagnosis results require only \textbf{one} run under the 
problem-triggering input.
All our performance results are obtained by taking average of \textbf{ten} runs, 
with the variation among different runs always less than 5\%.

%More discussions about all the parameters/thresholds presented above, including
%how to set them and how sensitive they are, are discussed in Section
%\ref{sec:sensi}.

\subsection{Coverage Results}
\label{sec:coverage}
Overall, \Tool provides good diagnosis coverage, as shown by the check-marks in Table~\ref{tab:benchmarks}
(the ``Did \Tool Identify ..?'' columns). 
\Tool identifies the correct root cause for \textbf{all} \allbugs benchmarks, and 
suggests fix strategies that match what developers took in practice
for 33 out of \allbugs cases.

@@

Second, the fix strategy taken by developers is related to
what suggested by \Tool.
The root-cause loops in 
Collections bugs \#407, \#408, and \#425 all conduct frequent linear searches in arrays.
\Tool suggests data-structure changes for these three cases. Developers' patches 
still keep the original data structures and the original buggy loops, but they
did use hash-sets, which contain the same content as the arrays do,
to help conditionally skip the loops.

Third, \Tool cannot suggest fix strategy for 1* loops.
For GCC\#12322, \Tool correctly tells that the loop under study
does not contain any form of inefficiency and produce results in every 
iteration, and hence fails to suggest any fix strategy. In practice, GCC
developers decide to skip the loop, which will cause some programs compiled by
GCC
to be less performance-optimal than before. 
%However, GCC developers feel
%that it is worthwhile considering the slow-down caused by the original loop.

@@

As shown in Table \ref{tab:performance}, 
the performance of \Tool is good. The overhead is consistently under or around 5\% 
except for one benchmark, Mozilla\#347306. 
We believe \Tool is promising for potential production
run usage.
We can easily further lower the overhead through sparser sampling.
%the current diagnosis results are obtained by running the
%program only \textbf{once} under the problem-triggering workload.
%If we use sparser sampling, more failure runs will be needed to obtain good
%diagnosis results.

@@

The performance benefit of sampling is huge.
Without sampling, redundancy
analysis lead to over 100X slowdown for six benchmarks.
The benefit of static optimization is also non-trivial. 
For example, for MySQL\#15811 and MySQL\#27287, static analysis alone
(i.e., no run-time overhead) can
judge that they do not contain cross-iteration redundancy: the computation of 
each iteration depends on loop induction variables, which are naturally different
in different iterations. 
As another example, the buggy loops of MySQL\#27287 and MySQL\#15811 access 
arrays. 
After changing to tracking the initial and ending memory-access addresses
of the array, instead of the content of the whole array accesses,
the overhead is reduced from 12.18\% to 0.20\% for MySQL\#27287, 
and from 20.53\% to 0.35\% for MySQL\#15811 respectively 
(sampling is conducted consistently here).

\subsection{Parameter Setting and Sensitivity}
\label{sec:sensi}
\noindent\textbf{Sampling rates}
We have tried different sampling rates for redundancy analysis.
Intuitively, sparser sampling leads to lower overhead but worse diagnosis
results. Due to space constraints, we briefly summarize the results below.

When we lower the sampling rate from 1/100 to 1/1000 
in cross-loop redundancy analysis,
among all the benchmarks in Table \ref{tab:performance},
Mozilla\#416628 incurs the largest overhead (merely 4.51\%). 
When we lower the sampling rate from 1/1000 to 1/10000
in cross-iteration redundancy analysis,
among all the benchmarks in Table \ref{tab:performance},
Mozilla\#347306 has the largest overhead (merely 7.38\%). 
%In fact, Mozilla347306 is the only one whose overhead is larger than 2\%. 
In both cases,
the diagnosis results remain 
the same for all but GCC\#12322, where too few samples are available
to judge redundancy.
%If we increase the sampling rate to 1/100, we will 
%have two benchmarks whose overhead is larger than 30\%.

\noindent\textbf{Resultful and redundancy rate}
Our default setting should work in most cases.
In fact, the diagnosis results are largely {\bf in}sensitive to the threshold
setting. For example, the results would remain the same when
changing the redundancy rate threshold from 0.5 to any value between about
0.1 and 0.66. We will have 1 more false negative and 1 fewer benign false positive, 
when the rate is 0.7. The trend is similar for resultless loop checking. 
Developers can adjust these thresholds. 
They can even get rid of thresholds, and only
use the raw values of resultful/redundancy rates to understand
the absolute and relative (in)efficiency nature of suspicious 
loops. Based on our experiments, the difference between efficient and inefficient
loops is obvious based on these rates.

### 2016-08-25 section/6_related.tex
slight change to figure 3 explanation
finish shrinking

\subsection{Performance Diagnosis}
Profilers are the most commonly used tools that help developers understand
performance
\cite{Zaparanuks:2012:AP:2254064.2254074,Coppa:2012:IP:2254064.2254076,
D'Elia:2011:MHC:1993498.1993559, 
Mytkowicz:2010:EAJ:1806596.1806618,
Ravindranath:2012:AMA:2387880.2387891,
Jovic:2011:CMY:2048066.2048081,IntroPerf}.
Different from our work, profiling aims to tell where 
computation resources are spent, 
not where and why computation resources are wasted. 
The root cause code region of a performance problem often is not inside
the top-ranked function in the profiling result \cite{SongOOPSLA2014}.
Even if it is, developers still need to spend a lot of effort to understand
whether and what kind of computation inefficiency exists.

Recently, tools that go beyond profiling and provide more automated analysis
have been proposed.
StackMine~\cite{Han:2012:PDL:2337223.2337241} can
identify slow call-stack patterns inside event handlers. The work by
\citet{TaoAsplos2014} analyzes system traces to understand 
performance impact propagation and 
causality relationship among different system components. 
X-ray~\cite{Attariyan:2012:XAR:2387880.2387910} helps identify inputs
or configuration entries that are most responsible for performance problems.
Although these techniques are all very useful, 
they target different problems from \Tool. \Tool targets 
inefficient loops, a common
inefficiency problem that contributes to
about two thirds of real-world user-perceived performance problems studied
by previous work \cite{SongOOPSLA2014}, and tries to pin-point the exact
root cause and provide fix-strategy suggestions.

\Tool is most related to
the recent statistical performance debugging work
\citep{SongOOPSLA2014}, both trying to identify source-code level root causes
for user-perceived performance problems. 
This previous work identifies which loop is most correlated with 
a performance symptom through statistical analysis, 
but cannot answer whether or 
what type of inefficiency this loop contains.
\Tool complements it by
providing detailed root cause information and fix strategy suggestions through
program analysis.

\subsection{Performance Bug Detection}

@@

As discussed in 
Section \ref{sec:intro}, these tools are all useful in improving software
performance, but are not suitable for performance diagnosis.
With different design goals from \Tool, these bug detection tools are not 
guided by any specific
performance symptoms. Consequently, they take different coverage-accuracy
trade-offs from \Tool. \Tool tries to cover a wide variety of root-cause 
categories and is more aggressive in identifying root-cause categories, because
it is only applied to a small number of loops that are known to be highly
correlated with the specific performance symptom under study.
Performance-bug detection tools has to be more conservative and tries hard
to lower false positive rates, because it needs to apply its analysis to the
whole program, instead of just a few loops. This requirement causes bug
detection tools to each focus on a specific root-cause category.
%In fact, most inefficient loops in our study are very difficult to be detected
%by a generic performance bug detectors --- it is very difficult to prove them to
%be inefficient without application-specific domain knowledge.
%For example, only a couple of inefficient loops out of the 45 studied
%in Table \ref{tab:root} can be detected by recent static inefficient
%loop checkers
%\cite{CARAMEL,IsilDillig.PLDI15}.
Performance bug detection tools also do not aim to provide fix suggestions.
For the few that do provide \cite{CARAMEL}, they only focus on very specific
fix patterns, such as adding a break into the loop. 
In addition, dynamic performance bug detectors do not try to achieve any
performance goals. None of them has tried applying sampling to their
bug detection and often leads to 10X slowdowns or more.

\subsection{Other Techniques to Fight Performance Bugs}

>>>>

Profilers are the most commonly used tools that help developers understand
performance
\cite{Zaparanuks:2012:AP:2254064.2254074,Coppa:2012:IP:2254064.2254076,
D'Elia:2011:MHC:1993498.1993559, 
Mytkowicz:2010:EAJ:1806596.1806618,
Ravindranath:2012:AMA:2387880.2387891,
Jovic:2011:CMY:2048066.2048081,IntroPerf}.
They aim to tell where 
computation resources are spent, 
not where and why computation resources are wasted. 
The root-cause code region of a performance problem often is not inside
the top-ranked function in the profiling result \cite{SongOOPSLA2014}.
Even if it is, developers still need to spend a lot of effort to understand
whether and what kind of computation inefficiency exists.

Recently proposed tools go beyond profiling and provide more automated analysis.
They can identify slow call-stack patterns inside event handlers
\cite{Han:2012:PDL:2337223.2337241}, help understand performance causality
relationship among system components
\citet{TaoAsplos2014}, identify inputs 
or configuration entries that are most responsible for performance problems
\cite{Attariyan:2012:XAR:2387880.2387910},
and estimate the performance impact of any
potential optimization at any point of a multi-threaded program
\cite{coz.sosp15}. 
They all target different problems from \Tool. 
\comment{
\Tool targets 
inefficient loops, a common
inefficiency problem that contributes to
about two thirds of real-world user-perceived performance problems studied
by previous work \cite{SongOOPSLA2014}, and tries to pin-point the exact
root cause and provide fix-strategy suggestions.
}

\Tool is most related to
the recent statistical performance debugging work
\citep{SongOOPSLA2014}, both trying to identify source-code level root causes
for user-perceived performance problems. 
This previous work identifies which loop is most correlated with 
a performance symptom through statistical analysis, 
but cannot answer whether or 
what type of inefficiency this loop contains.
\Tool complements it by
accurately pointing out whether the suspicious loop is inefficient,
which type of inefficiency a loop contains if any, and 
what is the best fix strategy.

@@

As discussed in 
Section \ref{sec:intro}, these tools are all useful, 
but are not suitable for performance diagnosis.
Bug detectors are not guided by any specific
performance symptoms. Consequently, they take different coverage-accuracy
trade-offs from \Tool. \Tool tries to cover a wide variety of root-cause 
categories and is more aggressive in identifying root-cause categories, because
it is only applied to a few loops known to be highly
correlated with a specific performance symptom.
Performance-bug detection tools are more conservative and try hard
to lower false positive rates, because they need to process the
whole program, instead of just a few loops. This requirement causes bug
detectors to each focus on a specific root-cause category.
%In fact, most inefficient loops in our study are very difficult to be detected
%by a generic performance bug detectors --- it is very difficult to prove them to
%be inefficient without application-specific domain knowledge.
%For example, only a couple of inefficient loops out of the 45 studied
%in Table \ref{tab:root} can be detected by recent static inefficient
%loop checkers
%\cite{CARAMEL,IsilDillig.PLDI15}.
Bug detectors also do not aim to provide fix suggestions.
For the few that do provide \cite{CARAMEL}, they only focus on very specific
fix patterns, such as adding a break into the loop. 
In addition, dynamic performance bug detectors often lead to 10X slowdowns or 
more, and never tried sampling.

Automated tools have been developed to detect inefficient loop bugs
\cite{Alabama, CARAMEL, IsilDillig.PLDI15}. 
As discussed above, these tools are good detection tools but not suitable for 
diagnosis. 
For example, Toddler~\cite{Alabama} only targets inefficient nested loops, and
hence can only cover about half of the bugs in our \emph{general} benchmark suite.
Being a dynamic tool, it also incurs 10X or more slowdowns, which is much more
expensive than \Tool. 
Caramel~\cite{CARAMEL} statically detects inefficient loops that can be fixed
by adding conditional-breaks. Very few bugs in Table \ref{tab:root} are like this.
CLARITY~\cite{IsilDillig.PLDI15} statically detects redundant traversal bugs, 
which arise if a program fragment repeatedly iterates over a data structure, such as an array or list, that has not been modified between successive traversals of the data structure.
Like Toddler, it targets nested loops.
We expect it to detect a sub-set of the cross-loop redundancy
loops and a sub-set of 0*1? resultless loops in our benchmark set.

### 2016-08-25 section/7_con.tex
check to icse format
finish shrinking

\section{Conclusion}
\label{sec:con}
Performance diagnosis is time consuming and also critical for 
complicated modern software. \Tool tries to automatically 
pin-point the root cause of
the most common type of real-world performance problems, inefficient loops,
and provide fix-strategy suggestions to developers. It achieves the 
coverage, accuracy, and performance goal of performance diagnosis by leveraging
(1) a comprehensive root-cause taxonomy; (2) a hybrid static-dynamic program
analysis approach; and (3) customized random sampling that is a natural fit for 
performance diagnosis.
Our evaluation shows that \Tool can accurately identify detailed root causes
of real-world inefficient loop problems and provide fix-strategy suggestions. 
Future work can further improve \Tool by providing more detailed fix
suggestions and providing more information to help diagnose and fix
1* loops.

\acks
This work is supported in part by NSF grants IIS-1546543, CNS-1514256, CCF-1439091, and CCF-1514189; 
and Alfred P. Sloan Research Fellowship.

>>>>

\section{Conclusion}
\label{sec:con}
Performance diagnosis is time consuming and also critical for 
complicated modern software. \Tool tries to automatically 
pin-point the root cause of
the most common type of real-world performance problems, inefficient loops,
and suggest fix strategies to developers. It achieves the 
coverage, accuracy, and performance goal by leveraging
(1) a comprehensive root-cause taxonomy; (2) a hybrid program
analysis approach; and (3) customized random sampling that is a natural fit for 
performance diagnosis.
Our evaluation shows that \Tool can accurately identify detailed root causes
of real-world inefficient loops and suggest fix strategies.
Future work can improve \Tool by providing more detailed fix
suggestions and more information to diagnose and fix
1* loops.

%\acks
%This work is supported in part by NSF grants IIS-1546543, CNS-1514256, CCF-1439091, and CCF-1514189; 
%and Alfred P. Sloan Research Fellowship.

### 2016-08-25 section/tab_root.tex
check in Linhai's updates
finish shrinking

\begin{table*}[tb!]
%\begin{adjustwidth}{-.5in}{-.5in}
\small
\centering
{
\begin{tabular}{lccccccccccccc}
\hline
                      & Apache &Chrome & GCC  & Mozilla & MySQL &&M$_{\text{emoization}}$  & B$_{\text{atching}}$   &  C & S  & O$_{\text{ther}}$ && Total\\
\cmidrule{2-6}
\cmidrule{8-12}
                      & 11    & 4     & 8    & 12      & 10     && 12  & 12 & 4  & 9  & 8  && 45\\
\hline
\multicolumn{1}{l}{Cross-{\bf iteration} Redundancy}
&7&1&2&1&1&&\cca{7}&\cca{4}&0&0&\cca{1}&&12\\
\multicolumn{1}{l}{ Cross-{\bf loop} Redundancy}
&3&0&2&2&2&&\cca{5}&\cca{4}&\cca{0}&\cca{0}&\cca{0}&&9\\
\multicolumn{1}{l}{ {\bf 0*1?} Resultless}
&0&0&0&2&3&&\cca{0}&\cca{0}&\cca{4}&\cca{1}&\cca{0}&&5\\
\multicolumn{1}{l}{{\bf [0$|$1]*} Resultless}
&0&1&1&1&1&&\cca{0}&\cca{0}&\cca{0}&\cca{4}&\cca{0}&&4\\
\multicolumn{1}{l}{ {\bf 0*} Resultless}
&0&0&0&0&0&&\cca{0}&\cca{0}&\cca{0}&\cca{0}&\cca{0}&&0\\
\multicolumn{1}{l}{{\bf 1*} Resultless}
&1&2&3&6&3&&\cca{0}&\cca{4}&\cca{0}&\cca{4}&\cca{7}&&15\\
  %MySQL15811 is moved from 1* to here; consider it as fixed by M
\hline
\end{tabular}
}
%\end{adjustwidth}
\caption{The distribution among different applications and different fix strategies for bugs with each root-cause category.
(S: conditionally skip the loop; C: change the data structure)
}
\label{tab:root}
\end{table*}

>>>>

\begin{table*}[tb!]
%\begin{adjustwidth}{-.5in}{-.5in}
\small
\centering
{
\begin{tabular}{lccccccccccccc}
\hline
                      & Apache &Chrome & GCC  & Mozilla & MySQL &&M$_{\text{emoization}}$  & B$_{\text{atching}}$   &  C & S  & O$_{\text{ther}}$ && Total\\
\cmidrule{2-6}
\cmidrule{8-12}
\# of Bugs            & 11    & 4     & 8    & 12      & 10     && 12  & 12 & 4  & 9  & 8  && 45\\
\hline
\multicolumn{1}{l}{Cross-{\bf iteration} Redundancy}
&7&1&2&1&1&&\cca{7}&\cca{4}&0&0&\cca{1}&&12\\
\multicolumn{1}{l}{ Cross-{\bf loop} Redundancy}
&3&0&2&2&2&&\cca{5}&\cca{4}&\cca{0}&\cca{0}&\cca{0}&&9\\
\multicolumn{1}{l}{ {\bf 0*1?} Resultless}
&0&0&0&2&3&&\cca{0}&\cca{0}&\cca{4}&\cca{1}&\cca{0}&&5\\
\multicolumn{1}{l}{{\bf [0$|$1]*} Resultless}
&0&1&1&1&1&&\cca{0}&\cca{0}&\cca{0}&\cca{4}&\cca{0}&&4\\
\multicolumn{1}{l}{ {\bf 0*} Resultless}
&0&0&0&0&0&&\cca{0}&\cca{0}&\cca{0}&\cca{0}&\cca{0}&&0\\
\multicolumn{1}{l}{{\bf 1*} Resultless}
&1&2&3&6&3&&\cca{0}&\cca{4}&\cca{0}&\cca{4}&\cca{7}&&15\\
  %MySQL15811 is moved from 1* to here; consider it as fixed by M
\hline
\end{tabular}
}
%\end{adjustwidth}
\caption{Distribution among different applications and fix strategies for bugs with each root-cause category.
\footnotesize{
(C: change data structure; S: conditionally skip loop; darker background means more correlation between root causes and fixes)
}
}
\label{tab:root}
\end{table*}
